EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-22 05_examples.tex
Added SciPost Physics Codebased (SPC) format to edipack_sp.tex Moved conclusions, acknowledgements and appendix to 06_....tex file.
SPC compiles: 55pages
CPC compiles: 49pages

In the anti-adiabatic limit, the Holstein interaction takes a
particularly simple form:
\begin{equation}\label{HlikeAttraction}
    H_{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
\end{equation}
which describes a local Hubbard-like attraction among electrons
(mediated by local phonons).
In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
enters in a Bipolaronic Insulating phase~\citep{Capone2006PRB} for our
choice of the coupling.

>>>>

In the anti-adiabatic limit, the Holstein interaction takes a
particularly simple form:
\begin{equation}\label{HlikeAttraction}
    H_{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
\end{equation}
which describes a local Hubbard-like attraction among electrons
(mediated by local phonons).
In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
enters in a Bipolaronic Insulating phase~\cite{Capone2006PRB} for our
choice of the coupling.

### 2025-05-22 06_conclusions_acknowledgement_appendix.tex
Added SciPost Physics Codebased (SPC) format to edipack_sp.tex Moved conclusions, acknowledgements and appendix to 06_....tex file.
SPC compiles: 55pages
CPC compiles: 49pages

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or
%% 5p,twocolumn, preprint, review
\documentclass[preprint,3p,10pt]{elsarticle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{makecell}
\usepackage{array}
\usepackage{stackengine}
\newlength\llength
\llength=1.38ex\relax
\usepackage[dvipsnames]{xcolor}
\usepackage{makecell}
\usepackage{subfiles}
\usepackage{comment}
\newcommand{\fixme}[1]{{\color{BrickRed} #1}}
\usepackage{xspace}

%% natbib.sty is loaded by default. natbib options with \biboptions{...}
\biboptions{sort&compress,super}

% Hypelinks in the document; settings
\usepackage[colorlinks=true,linkcolor=blue,citecolor=red]{hyperref}
% \usepackage[normalem]{ulem}

\usepackage{listings}
\lstdefinestyle{fstyle}{
  frame=lines,
  language=fortran,
  basicstyle=\footnotesize,
  stringstyle=\ttfamily,
  commentstyle=\itshape,
  fontadjust=true,
  keywordstyle=\color{red},
  % morekeywords={*,...},
  mathescape,
  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
}

\lstdefinestyle{mypython}{
  frame=lines,
  language=python,
  basicstyle=\footnotesize,
  stringstyle=\ttfamily,
  commentstyle=\itshape,
  fontadjust=true,
  keywordstyle=\color{red},
  % morekeywords={*,...},
  mathescape,
  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
}

\definecolor{mymauve}{rgb}{0.58, 0, 0.82}
\lstdefinestyle{mybash}{
  frame=lines,
  language=bash,
  basicstyle=\footnotesize,
  captionpos=b,
  stringstyle=\color{mymauve},%\ttfamily,
  commentstyle=\itshape,
  fontadjust=true,
  keywordstyle=\bfseries,
  % It would be nice to have 'conda' here,
  % but then 'conda-forge' gets highlighted too.
  morekeywords={*,git,mkdir,cmake,make,pip},
  mathescape,
  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
}

\lstdefinestyle{cstyle}{
  frame=lines,
  language=c,
  basicstyle=\footnotesize,
  stringstyle=\ttfamily,
  commentstyle=\itshape,
  fontadjust=true,
  keywordstyle=\color{red},
  % morekeywords={*,...},
  mathescape,
  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
}

% % MINTED:
% % \usepackage[cache=true,cachedir=minted-cache]{minted}
% % \usepackage[finalizecache=true,cachedir=minted-cache]{minted}
% \usepackage[frozencache=true,cachedir=minted-cache]{minted}
% \setminted[fortran]{linenos,mathescape,frame=lines,style=bw,framesep=1mm,
%   baselinestretch=1,fontsize=\footnotesize}

\usepackage{array}
\usepackage{tabularx}
\usepackage{ltablex}

\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}

\renewcommand{\arraystretch}{1.4}
% \newcolumntype{T}[1]{>{\tt\footnotesize}m{{#1}}}
% \newcolumntype{D}[1]{>{\it\footnotesize}m{#1}}
% \newcolumntype{M}[1]{>{\scriptsize}m{#1}}

\newcolumntype{T}[1]{>{\tt\footnotesize\raggedright\arraybackslash}p{#1}}
\newcolumntype{D}[1]{>{\it\footnotesize\raggedright\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\scriptsize\raggedright\arraybackslash}p{#1}}

\newcommand{\onlinecite}[1]{\nocite{#1}\!\!\!\citenum{#1}}

\newcommand {\note}[1]{{\color{blue} [{\bf NOTE}: \bf #1]}}
\newcommand {\aac}[1]{{\color{red} [{\bf AA}: \bf #1]}}
\newcommand {\new}[1]{{\color{blue}\it #1}}
%\newcommand {\new}[1]{{#1}}
% \DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}

\usepackage[inline]{showlabels}

%Reference to a given labelled equation
%and definition of a bib. element.
%-------------------------------------------
\newcommand{\equ}[1]
{Eq.\,(\ref{#1})}

\newcommand{\figu}[1]
{Fig.\,\ref{#1}}

\newcommand{\secu}[1]
{Sec.\,\ref{#1}}

\newcommand{\ket}[1]
{|#1\rangle}

\newcommand{\bra}[1]
{\langle #1|}

\newcommand{\sgn}
{\mathop{\mathrm{sgn}}}

%SIMBOLI VARI
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\bcen{\begin{center}}
\def\ecen{\end{center}}

\def\a{\alpha}       \def\b{\beta}   \def\g{\gamma}   \def\d{\delta}
\def\e{\varepsilon}  \def\z{\zeta}   \def\h{\eta}     \def\th{\theta}
\def\k{\kappa}       \def\l{\lambda} \def\m{\mu}      \def\n{\nu}
\def\x{\xi}          \def\p{\pi}     \def\r{\rho}     \def\s{\sigma}
\def\t{\tau}         \def\f{\varphi} \def\ph{\varphi} \def\c{\chi}
\def\ps{\pi}        \def\y{\upsilon}\def\o{\omega}   \def\si{\varsigma}
\def\G{\Gamma}       \def\D{\Delta}  \def\Th{\Theta}  \def\L{\Lambda}
\def\X{\Xi}          \def\P{\Pi}     \def\Si{\Sigma}  \def\F{\Phi}
\def\Ps{\Psi}        \def\O{\Omega}  \def\Y{\Upsilon} \def\lg{\langle}

\def\PP{{\cal P}}\def\EE{{\cal E}}\def\MM{{\cal M}} \def\VV{{\cal V}}
\def\CC{{\cal C}}\def\FF{{\cal F}}\def\HH{{\cal H}}\def\WW{{\cal W}}
\def\TT{{\cal T}}\def\NN{{\cal N}}\def\BB{{\cal B}} \def\II{{\cal I}}
\def\RR{{\cal R}}\def\LL{{\cal L}}\def\JJ{{\cal J}} \def\OO{{\cal O}}
\def\DD{{\cal D}}
\def\AA{{\cal A}}
\def\GG{{\cal G}} \def\SS{{\cal S}}
\def\ZZ{{\cal Z}} \def\UU{{\cal U}}
\def\SB{{\cal S}{\cal B}}
\def\aa{{\V \a}}
\def\hh{{\V h}}\def\HHH{{\V H}}
%\def\AA{{\V A}}
%\def\GG{{\V G}}\def\BB{{\V B}}\def\aaa{{\V a}}\def\bbb{{\V b}}
\def\nn{{\V \n}}\def\pp{{\V p}}\def\mm{{\V m}}\def\qq{{\bf q}}
\def\RRR{\mathbb{R}} \def\CCC{\mathbb{C}} \def\NNN{\mathbb{N}}
\def\ZZZ{\mathbb{Z}}
%\def\TTT{\hbox{\msytw T}}

\def\ul{\underline}
\def\=={\equiv}
\def\defi{{\buildrel def \over =}}
\def\lft{\left} \def\rgt{\right} \def\dpr{\partial} \def\der{{\rm d}}
\def\us{\underline \s} \def\ue{{\underline \e}}
\def\la{\left\langle}
\def\ra{\right\rangle}
\def\qed{\raise1pt\hbox{\vrule height5pt width5pt depth0pt}}
\def\iome{i\omega_n} \def\iom{i\omega} \def\iom#1{i\omega_{#1}}
\def\iomn{i\omega_n}
\def\epsk{\epsilon({\bf k})} \def\Ga{\Gamma_{\alpha}}
\def\Seff{S_{eff}}  \def\dinf{$d\rightarrow\infty\,$}
\def\cG0{{\cal G}_0}
\def\cG{{\cal G}}  \def\cU{{\cal U}}  \def\cS{{\cal S}}
\def\spinup{\uparrow} \def\spindown{\downarrow} \def\spindw{\downarrow}
\def\up{\uparrow} \def\down{\downarrow} \def\dw{\downarrow}

\def\Ak{{\bf A}} \def\Akt{{\bf A}(t)} \def\Ek{{\mathbf E}}
% \def\Im{\mbox{Im}}
\def\=={\equiv}
\def\defi{{\buildrel def \over =}} \def\nt{\widetilde{n}}
\def\Im{{\rm Im}} \def\Re{{\rm Re}} \def\Tr{{\rm Tr}}
\def\det{{\rm det}\,}

\def\ibra{\langle}
\def\iket{\rangle}

\def\ka{{\bf k}}
\def\vk{{\bf k}}
\def\qa{{\bf q}}
\def\vQ{{\bf Q}}
\def\vr{{\bf r}}
\def\q{{\bf q}}
\def\R{{\bf R}}
\def\vR{{\bf R}}
\def\kx{{ k_x}}
\def\ia{{\bf i}}
\def\ja{{\bf j}}

\usepackage{bbold}
\def\11{\mathbb{1}}
\def\00{\mathbf{0}}
\def\NAME{{\rm EDIpack}\xspace}
\newcommand{\shortrightarrow}{\mathrel{\mkern3mu\rightarrow\mkern}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\journal{Computer Physics Communications}

\begin{document}

\begin{frontmatter}

\title{EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems}
\author[a,b,c]{L.~Crippa*}
\author[a]{I.~Krivenko*}
\author[d]{S.~Giuli*}
\author[d]{G.~Bellomia*}
\author[c]{A.~Kowalski}
\author[e]{F.~Petocchi}
\author[f]{M.~Wallerberger}
\author[g]{G.~Mazza}
\author[h]{L.~de Medici}
\author[c,b]{G.~Sangiovanni}
\author[d,i]{M.~Capone*}
\author[i]{A.~Amaricci*}
% \author[]{A.~Scazzola}

% \cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}
\newcommand{\CNRIOM}{CNR-IOM, Istituto Officina dei Materiali,
  Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136
  Trieste, Italy}
\newcommand{\SISSA}{Scuola Internazionale Superiore di Studi Avanzati (SISSA),
  Via Bonomea 265, 34136 Trieste, Italy}
\newcommand{\ITPHamburg}{I. Institute of Theoretical Physics,
  University of Hamburg, Notkestrasse 9, 22607 Hamburg, Germany}
\newcommand{\WZBURG}{Institut f\"ur Theoretische Physik und
  Astrophysik,Universit\"at W\"urzburg, 97074 W\"urzburg, Germany}
\newcommand{\CTQMAT}{W\"urzburg-Dresden Cluster of Excellence ct.qmat, 01062 Dresden, Germany}
\newcommand{\Geneve}{Department of Quantum Matter Physics, University of
  Geneva, Quai Ernest-Ansermet 24, 1211 Geneva, Switzerland}
\newcommand{\UPISA}{Department of Physics ``E. Fermi'' University of
  Pisa, Largo B. Pontecorvo 3, 56127 Pisa, Italy}
\newcommand{\ESPCI}{LPEM, ESPCI Paris, PSL Research University, CNRS, Sorbonne Universit\'e, 75005 Paris, France}
\newcommand{\TUW}{Institure of Solid State Physics, TU Wien, 1040 Vienna, Austria}

\address[a]{\ITPHamburg}
\address[b]{\CTQMAT}
\address[c]{\WZBURG}
\address[d]{\SISSA}
\address[e]{\Geneve}
\address[f]{\TUW}
\address[g]{\UPISA}
\address[h]{\ESPCI}
\address[i]{\CNRIOM}
% \address[]{Politecnico di Torino, Turin, Italy}
\cortext[1]{Corresponding authors}
% \cortext[*] {Corresponding author:giuli@sissa.it}
% \cortext[*]{Corresponding author:bellomia@sissa.it}

\begin{abstract}

\end{abstract}

\begin{keyword}
  %% keywords here, in the form: keyword \sep keyword
  Exact Diagonalization \sep
  Quantum Impurity Models\sep  
  Strongly Correlated Electrons \sep  
  Dynamical Mean-Field Theory
\end{keyword}

\end{frontmatter}

% Computer program descriptions should contain the following
% PROGRAM SUMMARY.
\noindent
{\bf PROGRAM SUMMARY}
\begin{small}
  \noindent
  \\
  {\em Program Title:}  EDIpack                                        \\
  {\em Licensing provisions:} GPLv3\\
  {\em Programming language:}  Fortran, Python, C/C++\\
  {\em Classification:} 6.5, 7.4, 20 \\
  {\em Required dependencies:} CMake ($>=3.10.0$), Scifortran, MPI\\
  {\em Nature of problem:}. \\
  {\em Solution method:} .\\
\end{small}

\tableofcontents

\subfile{01_intro.tex}
% ##################################################################
% ##################################################################
% ##################################################################

\subfile{02_install.tex}

% ##################################################################
% ##################################################################
% ##################################################################

\subfile{03_edipack2.tex}

\subfile{04_cbinding.tex}

\subfile{05_examples.tex}

@@

%% References with bibTeX database:
% \section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{references}

>>>>

\documentclass[edipack2.tex]{subfiles}
\begin{document}

@@
